---
title: "ff_data_factsheet"
format: html
editor: visual
---

# Purpose

This file goes through the Forests and Finance data to answer the following questions:

- What is the UK financial sector's role in global deforestation?
- How has the finance landscape changed over time among UK-based FIs in the past decade?
- What prohibited commodities (i.e. soy, cocoa, beef and leather, and palm oil and derivative products) do UK FI investments contribute to?
- What kinds of finance do UK FIs use to fund deforestation risk companies?


```{r}
#| echo: false
#| warnings: false
#| include: false

##### install and load packages #####
rm(list=ls())

# load packages
library(tidyverse)
# extract currencies from string
library(readxl)
library(readr)
library(ggplot2)
library(magrittr)
library(janitor)
library(simplermarkdown)

#### define paths ####
user <- Sys.getenv("USERNAME")
# specify project folder
main <- paste0("C:/Users/", user, "/Documents/Github/treasury")
dataraw <- paste(main, "dataraw", sep = "/")
dataout <- paste(main, "dataout", sep = "/")
temp <- paste(main, "temp", sep = "/")
```

```{r}
#| echo: false
#| warnings: false
#| include: false

# load ff data
ff <- paste(dataraw,
            "ForestsAndFinance Agriculture.csv",
            sep = "/") %>%
  read_delim() %>%
  clean_names() %>%
  mutate(type_short = case_when(
    type %in% c("Bondholding", "Shareholding") ~ "Investment",
    T ~ "Credit"
  )) %>%
  relocate(type_short, .after = type)
# shareholding and bondholding == investment
# all others == credit

colnames(ff)

# ff uk-headquartered only data
ff_uk <- ff %>%
  filter(country == "United Kingdom",
         bank == "HSBC") %>%
  group_by(type_short) %>%
  summarise(total = sum(amount_usd_millions, na.rm = T))


#### general questions/questions for ward ####
# why are there duplicate deals almost?
# what does amount_usd_millions mean? is it the slice ($ amount) of the deal the FI is involved in? is it their profit?
  # why are there certain deals/observations with amounts == 0 
  # even if opened into excel, there are some that are just small amounts, some are truly 0 
# what does the underlying (deal data) data look like?

# are these segment adjusted (e.g. income/value or whatever attributed to deforestation-related activities?)
# how is the DD data created/derived/different from FF?
# DD data - how were these variables constructed?
# DD data - how are profits/income derived from shareholdings?
  # maybe check the methodology
```
